Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-25 paper.tex
Remove comment
No new line after correspondence email address
Remove highlights

% Contact information of the corresponding author (Add [2] after \corres if
% there are more than one corresponding author.)
\corres[1]{\hspace{-1em} Correspondence: martin.wosnik@unh.edu;
    \linebreak Tel.: +1-603-862-1891}

@@

\includegraphics[width=0.9\textwidth]{figures/perf_re_dep}
%Please use scientific notation in the figure. for instance, please revise 1e6 to \times 10^6
\caption{\hl {UNH-RVAT} measured mean power (\textbf{a}) and drag (\textbf{b})
    coefficients at $\lambda=1.9$ plotted \textit{versus} the Reynolds number. Error
    bars indicate expanded uncertainty estimates for 95\% confidence, which for
    $C_P$ is dominated by systematic error estimates from the torque transducer
    operating at the lower end of its measurement range.}

@@

    \includegraphics[width=0.9\textwidth]{figures/all_foils_re_dep}
 % Please use scientific notation in the figure. for instance, please revise 1e5 to \times 10^5 
    \caption{\hl {Normalized maximum} lift coefficient (\textbf{a}), drag coefficient
        (\textbf{b}), and lift-to-drag ratio (\textbf{c}) computed by XFOIL at
        various $Re_c$  for each profile.}

@@

    \includegraphics[width=0.8\textwidth]{figures/cft_re_dep_foils}
%Please use scientific notation in the figure. for instance, please revise 1e6 to \times 10^6
    \caption{\hl {Reynolds} number dependence of the normalized peak torque
        coefficient calculated from static foil coefficients and blade kinematics,
        compared to experimental data from a cross-flow turbine. Note that the
        experimental data represents the mean torque coefficient, not the maximum.}

>>>>

% Contact information of the corresponding author (Add [2] after \corres if
% there are more than one corresponding author.)
\corres[1]{\hspace{-1em} Correspondence: martin.wosnik@unh.edu; Tel.:
    +1-603-862-1891}

@@

\includegraphics[width=0.9\textwidth]{figures/perf_re_dep}

\caption{UNH-RVAT measured mean power (\textbf{a}) and drag (\textbf{b})
    coefficients at $\lambda=1.9$ plotted \textit{versus} the Reynolds number. Error
    bars indicate expanded uncertainty estimates for 95\% confidence, which for
    $C_P$ is dominated by systematic error estimates from the torque transducer
    operating at the lower end of its measurement range.}

@@

    \includegraphics[width=0.9\textwidth]{figures/all_foils_re_dep}

    \caption{Normalized maximum lift coefficient (\textbf{a}), drag coefficient
        (\textbf{b}), and lift-to-drag ratio (\textbf{c}) computed by XFOIL at
        various $Re_c$  for each profile.}

@@

    \includegraphics[width=0.8\textwidth]{figures/cft_re_dep_foils}

    \caption{Reynolds number dependence of the normalized peak torque
        coefficient calculated from static foil coefficients and blade kinematics,
        compared to experimental data from a cross-flow turbine. Note that the
        experimental data represents the mean torque coefficient, not the maximum.}
